EvoSwarm: An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-05-07 draft.tex
Details checked and revised, closes #7 (when you add to response letter)

For local experiments we have deployed the EvoSwarm application in a
Desktop PC with AMD Ryzen 9 3900x 12-core processor with 24 threads 
and 16 GB RAM. We used Docker version 19.03.3, build a872fc2f86, and docker-compose version 1.21.0, 
in Ubuntu Linux 18.04, and Python 3.7.5 code. Container images and Docker compose file are available at
(https://hub.docker.com/u/mariosky), and (https://github.com/mariosky/EvoSwarm) respectively. 
The BOBB experiments were performed with COCO \cite{hansen2016coco} version bbob.v15.03 in python, 
the plots were produced with version 2.3.2.

>>>>

For local experiments we have deployed the EvoSwarm application in a
Desktop PC with an AMD Ryzen 9 3900x 12-core processor with 24 threads 
and 16 GB RAM. We used Docker version 19.03.3, build a872fc2f86, and docker-compose version 1.21.0, 
in Ubuntu Linux 18.04; coce is run using Python 3.7.5. Container images and the docker-compose file are available at
\url{https://hub.docker.com/u/mariosky}, and \url{https://github.com/mariosky/EvoSwarm} respectively. 
The BOBB experiments were performed with COCO \cite{hansen2016coco} version bbob.v15.03 in Python, 
the plots were produced with version 2.3.2. % Are we using BBOB plots? - JJ
